### 2021-04-15 Chapter-5/Chapter-5.tex
Updates from Overleaf

\subsection{Cryptography Libraries}
For symmetric ciphers, we evaluate \ctool{} on three types of AES implementations. For mebedTLS, we evaluate AES-NI and the reference implementation. We do not find any leakage sites in the AES-NI version. On the other hand, the reference implementation has several leakage sites. The bitsliced version from OpenSSL and wolfSSL should be resistant to side-channel attacks. However, we find they only adopt the protection in the encryption function but leave the key expansion function unprotected. The T-Table implementation has side-channel leakage sites in both the key expanding function and the actually encryption function. The result is similarly to the previous work.

We use a fixed RSA blinding value during the evaluation to avoid non-deterministic behaviors. We compare the result with previous work and find \ctool{} can identify all the leaked functions reported in the previous work.

\begin{table}[!ht]
\centering\tiny\scriptsize
\caption{Leakages in RSA implemented by OpenSSL 1.1.0f}\label{tab:RSAOpenSSL1.1.0f}
%\resizebox{\columnwidth}{!}{
\begin{tabular}{llrr}
\hline
\textbf{File}  & \textbf{Function} & \textbf{\# Leaked Bits} & \textbf{Fixed in OpenSSL 1.1.1} \\\hline
bn\_lib.c& BN\_num\_bits\_word&*&CF\\
bn\_lib.c& BN\_num\_bits\_word&*&CF\\
bn\_lib.c& BN\_num\_bits\_word&17.2 &DA\\
bn\_lib.c& bn\_correct\_top&*&CF\\
bn\_lib.c& BN\_ucmp&*&CF\\
ct\_b64.c& \_\_udivdi3&5.9 &CF\\
bn\_div.c& BN\_div&*&CF\\
bn\_gcd.c& int\_bn\_mod\_inverse&1.0 &CF\\
bn\_gcd.c& int\_bn\_mod\_inverse&7.9 &CF\\
bn\_gcd.c& int\_bn\_mod\_inverse&8.2 &CF\\
bn\_gcd.c& int\_bn\_mod\_inverse&14.9 &CF\\
bn\_gcd.c& int\_bn\_mod\_inverse&9.2 &CF\\
bn\_lib.c& BN\_num\_bits\_word&*&DA\\
bn\_lib.c& BN\_num\_bits\_word&12.6 &CF\\
bn\_lib.c& BN\_num\_bits\_word&*&DA\\
bn\_lib.c& BN\_num\_bits\_word&*&DA\\
bn\_div.c& BN\_div&17.2 &CF\\
bn\_div.c& BN\_div&11.9 &CF\\
bn\_div.c& BN\_div&3.8 &CF\\
bn\_exp.c& BN\_mod\_exp\_mont\_consttime&1.0 &CF\\
bn\_exp.c& BN\_mod\_exp\_mont\_consttime&1.0 &CF\\
bn\_mont.c& BN\_from\_montgomery\_word&*&DA\\
bn\_mont.c& BN\_from\_montgomery\_word&*&DA\\
bn\_mont.c& BN\_from\_montgomery\_word&*&DA\\
bn\_mont.c& BN\_from\_montgomery\_word&*&DA\\
bn\_mont.c& BN\_from\_montgomery\_word&*&DA\\
bn\_asm.c& bn\_sqr\_comba8&*&CF\\
bn\_asm.c& bn\_mul\_comba8&*&CF\\
bn\_mont.c& BN\_from\_montgomery\_word&0.0 &CF\\
bn\_div.c& BN\_div&0.3 &CF\\
bn\_div.c& BN\_div&0.3 &CF\\
\hline
\end{tabular}
%}
\renewcommand{\baselinestretch}{1.0}\selectfont
\end{table}
\subsection{Machine Learning Applications}
In the section, we demonstrate an attack that can recover the deep learning model inference output by the controlled-channel attack. Running the machine learning inference engine inside the enclave is a typical scenario for machine learning as service. The machine learning service provider upload the the trained model into an enclave running on the cloud platform and provide machine learning service to a third party user. With the help of the enclave, both the model and the user's inferred result is protected from the outside. However, we will show that the above information can be easily retrieved from the untrusted world through the side-channel attack.

>>>>

\subsection{Cryptography Libraries}
AES encryption can be divided into three steps. In the first step, the round keys are derived from the encryption keys called the AES key schedule, and the state array is initialized with the plain-text and the initial round step. In the second step, the AES performs eleven rounds of state manipulation. In the final stage, the state array is copied out as the encrypted data.
The reference implementation uses lookup tables in the first two steps. Intuitively, the implementation is vulnerable to side-channel attacks. There are some mitigated versions of AES. We evaluate \ctool{} on three variants of AES implementations: the reference implementation, the bit-sliced version, and the AES-NI implementation.
For mebedTLS, we evaluate AES-NI and the reference implementation. We do not find any leakage sites in the AES-NI version. On the other hand, the reference implementation has several leakage sites. The bit-sliced version from OpenSSL and wolfSSL should be resistant to side-channel attacks. However, we find they only adopt the protection in the encryption function but leave the key expansion function unprotected. The T-Table implementation has side-channel leakage sites in both the key expanding function and the actually encryption function.

We use a fixed RSA blinding value during the evaluation to avoid non-deterministic behaviors during the execution. After that, we compare the result with the previous work~\cite{bao2021abacus,203878}. The result shows that \ctool{} can identify all the leakage sites reported in the previous work. In addition, \ctool{} identify new leakages in the private key decoded functions (\textsf{EVP\_DecodeUpdate}, \textsf{EVP\_DecodeBlock}) in OpenSSL 1.1.0f and OpenSSL 1.1.1.

\begin{table}[!ht]
\centering\tiny\scriptsize
\caption{Leaked Functions in RSA implemented by OpenSSL 1.1.0f}\label{chapter5:tab:RSAOpenSSL1.1.0f}
%\resizebox{\columnwidth}{!}{
\begin{tabular}{llrr}
\hline
\textbf{File}  & \textbf{Function} & \textbf{\# Leaked Bits} & \textbf{Fixed in OpenSSL 1.1.1} \\\hline
bn\_lib.c& BN\_num\_bits\_word&*&CF\\
bn\_lib.c& BN\_num\_bits\_word&*&CF\\
bn\_lib.c& BN\_num\_bits\_word&17.2 &DA\\
bn\_lib.c& bn\_correct\_top&*&CF\\
bn\_lib.c& BN\_ucmp&*&CF\\
ct\_b64.c& \_\_udivdi3&5.9 &CF\\
bn\_div.c& BN\_div&*&CF\\
bn\_gcd.c& int\_bn\_mod\_inverse&1.0 &CF\\
bn\_gcd.c& int\_bn\_mod\_inverse&7.9 &CF\\
bn\_gcd.c& int\_bn\_mod\_inverse&8.2 &CF\\
bn\_gcd.c& int\_bn\_mod\_inverse&14.9 &CF\\
bn\_gcd.c& int\_bn\_mod\_inverse&9.2 &CF\\
bn\_lib.c& BN\_num\_bits\_word&*&DA\\
bn\_lib.c& BN\_num\_bits\_word&12.6 &CF\\
bn\_lib.c& BN\_num\_bits\_word&*&DA\\
bn\_lib.c& BN\_num\_bits\_word&*&DA\\
bn\_div.c& BN\_div&17.2 &CF\\
bn\_div.c& BN\_div&11.9 &CF\\
bn\_div.c& BN\_div&3.8 &CF\\
bn\_exp.c& BN\_mod\_exp\_mont\_consttime&1.0 &CF\\
bn\_exp.c& BN\_mod\_exp\_mont\_consttime&1.0 &CF\\
bn\_mont.c& BN\_from\_montgomery\_word&*&DA\\
bn\_mont.c& BN\_from\_montgomery\_word&*&DA\\
bn\_mont.c& BN\_from\_montgomery\_word&*&DA\\
bn\_mont.c& BN\_from\_montgomery\_word&*&DA\\
bn\_mont.c& BN\_from\_montgomery\_word&*&DA\\
bn\_asm.c& bn\_sqr\_comba8&*&CF\\
bn\_asm.c& bn\_mul\_comba8&*&CF\\
bn\_mont.c& BN\_from\_montgomery\_word&0.0 &CF\\
bn\_div.c& BN\_div&0.3 &CF\\
bn\_div.c& BN\_div&0.3 &CF\\
\hline
\end{tabular}
%}
\renewcommand{\baselinestretch}{1.0}\selectfont
\end{table}
\subsection{Machine Learning Applications}
In the section, we demonstrate an attack that can recover the deep learning model inference output by the controlled-channel attack. Running the machine learning inference engine inside the enclave is a typical scenario for machine learning as service. The machine learning service provider upload the the trained model into an enclave running on the cloud platform and provide machine learning service to a third party user. With the help of the enclave, both the model and the user's inferred result is protected from the outside. However, we will show that the above information can be easily retrieved from the untrusted world through the side-channel attack.
